# Tidyverse / kableExtra pipelines

To really levarage the power of R for tables, you'll likely want to get in the habit of
creating pipelines that use functions from the `tidyverse` package to reshape or 
clean your data before piping that data into `kable` and `kableExtra` functions to 
create the table. This section will walk through some examples of this pipeline, and 
how it can provide a powerful approach for creating tables from data in R. 

## Example data

Again, this section uses a dataset from the `dslabs` package called "us_contagious_diseases".
You can load that data by loading the `dslabs` package (if you don't have it, you 
can install it with `install.packages("dslabs")`) and then using the `data` function
to load the dataset:

```{r}
library(dslabs)
data("us_contagious_diseases")
```

This dataset includes counts by states for various infectious diseases. It gives these 
counts by year over a several decades. It also gives the number of weeks for which that
state reported data that year and the population of the state that year (in case you'd
like to calculate rates):

```{r}
us_contagious_diseases %>% 
  slice(1:4)
```

One quick table we might want to create may be a table where each state is listed, 
with the range of years that the state reported data. This way, we can quickly see 
the years that each state reported cases for each disease, and if all 
states have data for the same number of years. 

To do this, we'll need to get a *summary* from each combination of state and disease, 
where we get the minimum and maximum values of `year` for that combination. Then, we
can paste those values together to get the year range. We can `select` just the
columns we need for the final table, getting rid of any extra columns we created
along the way to help with our calculation. Finally, this table will look much nicer
if we have a separate column for each disease (while "long" data is easier to work with
when coding, "wide" data often is clearer in a presentation format). The
`pivot_wider` can do that reshaping. 

Here's the full pipeline:

```{r}
us_contagious_diseases %>% 
  # Get the year range for each combination of state and disease
  # by grouping by these variables and then using summarize
  group_by(state, disease) %>% 
  summarize(earliest_year = min(year),
            latest_year = max(year)) %>% 
  # Use `mutate` to make a new column that presents this range more
  # nicely (the `unite` function could work here, too)
  mutate(years = paste0(earliest_year, "--", latest_year)) %>% 
  # Limit to just the data you want to present in the table
  select(state, disease, years) %>% 
  # Reshape the data, so that each disease gets its own column
  pivot_wider(names_from = "disease", values_from = "years") %>% 
  # Send to `kable` for formatting as a table
  kable(booktabs = TRUE) %>% 
  # Make the font size a bit smaller than the default, so the date ranges
  # will be shown on one line each
  kable_styling(font_size = 10)
```


