## Change column names

### Basics of changing column names

By default, each column will have the same name as the column name in the data
that is input to `kable`. You can easily change those, though, with the 
`col.names` option. You just put in a character vector with as many values as you 
have columns, giving the names you would prefer:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) 
```

### Changing formatting in column names

The `kableExtra` package includes a `row_spec` function. This will make changes to 
the formatting of a specific row in the table. 

You can use this for any row, and that includes the row with the column headers. 
The `kableExtra` conventions consider this as row 0.

For example, you can put the column headers in italics by setting `italic = TRUE`
in a `row_spec` call for row 0: 

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, italic = TRUE)
```

If you would like to underline the column headers, you can set `underline = TRUE` in the
`row_spec` call for row 0:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, underline = TRUE)
```

You can change the color of the column names by using the `color` option in the 
`row_spec` call:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, color = "dodgerblue")
```

This function uses the R colornames, so you can check out those at sites like
http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf. 
It will also accept colors specified by hexadecimal code in the "#BBBBBB" format:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, color = "#FF5733")
```

You can check out websites on hexadecimal color codes at places like 
https://htmlcolorcodes.com/ to learn more about using these conventions to specify 
the color.

If you'd like to change the background color and the text color, you can 
add a specification for the "background" option in the `row_spec` call for row 0:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, color = "white", background = "#FF5733")
```

You can change the font size of the column names, without changing the font size for
the rest of the table, with the `font_size` parameter in `row_spec` for row 0. The
default text size is somewhere in the "14" range, so pick larger numbers to make the
text larger in the column names and smaller numbers to make the text smaller.

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, font_size = 20)
```

### Adding footnotes to column names
