## Group rows

You might also want to show structure or grouping within your rows. There
are a number of functions in `kableExtra` that help with this. 

These examples will again use data derived from the "us_contagious_diseases" data
from the `dslabs` package. The following code will load that data and then create the
`per_hepa_latest_years` dataframe from it:

```{r}
library(tidyverse)
library(dslabs)
data("us_contagious_diseases")

per_hepa_latest_years <- us_contagious_diseases %>% 
  # Limit to states in the region of interest
  filter(state %in% c("California", "Oregon", "Washington")) %>% 
  # Limit to the two diseases of interest
  filter(disease %in% c("Pertussis", "Hepatitis A")) %>% 
  # Limit to the latest five years reported for each combination of 
  # state and disease
  group_by(state, disease) %>% 
  arrange(desc(year)) %>%
  slice(1:5) %>%
  # Calculate the average weekly count from the total yearly count and
  # the number of weeks reporting (should check data---does an 
  # 'unreported' week mean there were no cases that week?)
  ungroup() %>% 
  mutate(ave_weekly_count = count / weeks_reporting) %>%
  # Limit to only the data to show in the table
  select(state, disease, year, ave_weekly_count) %>% 
  # Reorder by year so that the earliest year comes first
  arrange(disease, state, year) %>% 
  # "Widen" the data for a nicer table
  pivot_wider(names_from = year, values_from = ave_weekly_count)
```

This dataframe  gives the average weekly counts of 
two diseases (separately) in three west coast states over the last five years of reporting. The 
code used to create this dataset is an extension of the code used in the section on 
adding top headings to tables---in this case, we're adding on data for a second disease. 

Here's what the dataframe looks like: 

```{r}
per_hepa_latest_years
```

When we create a table from this, we may want to group the rows by disease (or by state),
so that readers can see common factors in certain rows.

You can create those groupings using the `pack_rows` function. You will include one
of these for each of the groupings that you want to create. For example, here there's
one `pack_rows` to group the first three rows (all with measurements of Hepatitis A)
and a second `pack_rows` to group the fourth through six rows (all with measurements
of pertussis). For each `pack_rows` call, it gives the name that will be used for 
the grouping (this is the name that shows up as a label for those groups in the 
table) as well as the number of the line where the grouping should start (`start_row`)
and the line where it should end (`end_row`):

```{r}
per_hepa_latest_years %>% 
  select(-disease) %>% 
  kable(digits = 1) %>% 
  pack_rows("Hepatitis A", start_row = 1, end_row = 3) %>% 
  pack_rows("Pertussis", start_row = 4, end_row = 6)
```

