## Create a basic table

```{r message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
```

### Example data

You can read in some data from the `dslabs` package on infectious disease cases in 
US states and check it out:

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(dslabs)
data("us_contagious_diseases")

us_contagious_diseases %>% 
  slice(1:3)

us_contagious_diseases %>% 
  summary()
```

With this data, you can 
create a basic table with the total counts of pertussis by state over the period
of the data (1928--2011), limiting to the top 10 states. First, you can use `tidyverse`
code to create the dataframe with the data you'd like to show in the table:

```{r}
top_10_data <- us_contagious_diseases %>% 
  filter(disease == "Pertussis") %>% 
  group_by(state) %>% 
  summarize(total_count = sum(count)) %>% 
  arrange(desc(total_count)) %>% 
  slice(1:10) 
```

### Creating a basic table

Then, you can use the `kable` function to create a basic PDF table:

```{r}
top_10_data %>% 
  kable() 
```

The `booktabs = TRUE` option, if you include it in the `kable` function call, will give 
some cleaner default formatting for the table: 

```{r echo = 1:2}
top_10_data %>% 
  kable(booktabs = TRUE) 
```



