## Add a top header

You can also add headers above certain column names, to help distinguish groupings. 

For this section, we'll use an example based on the "us_contagious_diseases" data
from the `dslabs` package. The following code will load that data and then create the
`pertussis_latest_years` dataframe from it:

```{r}
library(tidyverse)
library(dslabs)
data("us_contagious_diseases")

pertussis_latest_years <- us_contagious_diseases %>% 
  # Limit to states in the region of interest
  filter(state %in% c("California", "Oregon", "Washington")) %>% 
  # Limit to the disease of interest
  filter(disease == "Pertussis") %>% 
  # Limit to the latest five years reported for each state
  group_by(state) %>% 
  arrange(desc(year)) %>%
  slice(1:5) %>%
  # Calculate the average weekly count from the total yearly count and
  # the number of weeks reporting (should check data---does an 
  # 'unreported' week mean there were no cases that week?)
  mutate(ave_weekly_count = count / weeks_reporting) %>%
  # Limit to only the data to show in the table
  select(state, year, ave_weekly_count) %>% 
  # Reorder by year so that the earliest year comes first
  arrange(year) %>% 
  # "Widen" the data for a nicer table
  pivot_wider(names_from = year, values_from = ave_weekly_count)
```

This dataframe gives average weekly counts of 
pertussis in three west coast states over the last five years of reporting. The 
code used to create this dataset from the original data is discussed in a previous
section of this book.

Previously, we created this table from the data:

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.")
```

We might want to add a top header over the five columns that show years, to distinguish
that those are all similar types of columns. With `kableExtra`, this can be added with 
the function `add_header_above`. The convention for this argument is to include a value
for `header` that's a vector; this vector will give the names to use for top-level headers
as well as the number of columns they should span. In this case, we'd like to not add 
anything over the "state" column, so we can use the marker `" "` to indicate that 
no top-level header should be added. For all the other columns, we'll add "Year". 
Since we only have one column (the first) that will lack a top-level header, and 
then five (the years) that will all get the same header ("Year"), we can express
that in the "header" argument as `c(" " = 1, "Year" = 5)`. In other words, don't 
have a top-level header for one column, and then have one named "Year" that spans
five columns. 

Here's the result:

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "Year" = 5))
```

In the `add_header_above` call, you'll need to make sure that you specify values
for all the columns in your table. In other words, all the numbers in that argument
should add up to the number of columns that you have. In this case, we have six
columns in the table (the "state" column plus each of the yearly ones). Since
5 + 1 = 6, we're good here. 

Here's another example, where separate headers are added for the first two then the
next three years: 

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "First two years" = 2, "Next three years" = 3))
```

Again, you can see that 1 + 2 + 3 = 6, so we've covered all of our columns in the 
table. 

If you want, you can even add headers on top of headers. Just keep adding calls to 
`add_header_above`, going from the header you want closest to the column names to the
top-most one you want. For example, you could add a header above both of the two 
top-level headers in the previous example with:

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "First two years" = 2, "Next three years" = 3)) %>% 
  add_header_above(header = c(" " = 1, "Year" = 5))
```

You can change the formatting of the header in the `add_header_above` call, as well. 
For example, you can change it to be in italics with `italic = TRUE`:

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "Year" = 5), 
                   italic = TRUE)
```

You can change the alignment, too. The default is to be centered over the columns that
it spans, but you can change that with `align`. For example, `align = "l"` would change 
it to be left-aligned: 

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "Year" = 5), 
                   align = "l")
```

You can change the color of both the text and the background color for this new
header section with teh `color` and `background` arguments, respectively: 

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "Year" = 5), 
                   color = "white",
                   background = "lightsalmon")
```

You can change the angle of the text for the new header with `angle`:

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "Year" = 5), 
                   angle = -45)
```

If you'd like the text for a column to have a line break, you can include the 
code for a new line ("\n") inside the column name:

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "Year\n(Georgian calendar)" = 5))
```

If you have more than one top-level header, you may want to change the amount
of separation between each group. You can do that with the `line_sep` argument. 
Here is the example table where separate top-level headers are added for the 
first two years versus the last three from earlier: 

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "First two years" = 2, "Next three years" = 3))
```

If you set `line_sep = 0`, then you'll see that there's no space between the two 
header sections, so the line under the two headers runs together into one line:

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "First two years" = 2, "Next three years" = 3),
                   line_sep = 0)
```

On the other hand, if you set `line_sep` to a value higher than it's default of 3, 
you can increase the separation in the headers: 

```{r}
pertussis_latest_years %>% 
  kable(digits = 1,
        caption = "Average weekly number of cases of pertussis in west coast states for the last five years of reporting.") %>% 
  add_header_above(header = c(" " = 1, "First two years" = 2, "Next three years" = 3),
                   line_sep = 10)
```

