## Bold columns or rows

When tables have a lot of content, you may want to highlight elements to draw attention to them. This example uses data from the `AmesHousing` package.

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(AmesHousing)

top_neighborhoods <- make_ames() %>%
  filter(Year_Sold == 2010) %>%
  group_by(Neighborhood) %>%
  summarize(Home_Sales = n(),
            Total = scales::dollar(sum(Sale_Price))) %>%
  slice_max(order_by = Home_Sales, n=8) 
```

The column_spec() function allows the selection of a column and then a specification for the look. For example, this is a **bold** treatment for the third column.

```{r}
top_neighborhoods %>%
  kable() %>%
  kable_styling() %>%
  column_spec(3, bold = T) 
```

The row_spec() function allows the selection of rows and a specification for a style. 
For greater emphasis, this example sets a background fill color and the font color. 

```{r}
top_neighborhoods %>%
  kable() %>%
  kable_styling() %>%
  row_spec(3:4, bold = T, color = "white", background = "#D7261E")
```
