## Change column names

### Basics of changing column names

By default, each column will have the same name as the column name in the data
that is input to `kable`. You can easily change those, though, with the 
`col.names` option. You just put in a character vector with as many values as you 
have columns, giving the names you would prefer:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) 
```

### Changing formatting in column names

The `kableExtra` package includes a `row_spec` function. This will make changes to 
the formatting of a specific row in the table. 

You can use this for any row, and that includes the row with the column headers. 
The `kableExtra` conventions consider this as row 0.

For example, you can put the column headers in italics by setting `italic = TRUE`
in a `row_spec` call for row 0: 

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, italic = TRUE)
```

If you would like to underline the column headers, you can set `underline = TRUE` in the
`row_spec` call for row 0:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, underline = TRUE)
```

You can change the color of the column names by using the `color` option in the 
`row_spec` call:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, color = "dodgerblue")
```

This function uses the R colornames, so you can check out those at sites like
http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf. 
It will also accept colors specified by hexadecimal code in the "#BBBBBB" format:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, color = "#FF5733")
```

You can check out websites on hexadecimal color codes at places like 
https://htmlcolorcodes.com/ to learn more about using these conventions to specify 
the color.

If you'd like to change the background color and the text color, you can 
add a specification for the "background" option in the `row_spec` call for row 0:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, color = "white", background = "#FF5733")
```

You can change the font size of the column names, without changing the font size for
the rest of the table, with the `font_size` parameter in `row_spec` for row 0. The
default text size is somewhere in the "14" range, so pick larger numbers to make the
text larger in the column names and smaller numbers to make the text smaller.

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, font_size = 20)
```

### Adding footnotes to column names

You can also add footnotes based on a column name. This gets just a touch more
complex, because what you actually need to do is *rename* the column name to include
the footnote marker in the column's name. 

These markers can be added with 
functions that start with `footnote_marker`. For example, `footnote_marker_alphabet`
gives letters for each footnote. The other options are `footnote_marker_number` and
`footnote_marker_symbol`. You can add one of these to a column name directly in 
the `col.names` vector of column names by using `paste0` to add the marker on to the
existing column name. You'll put in `1` for the argument for the first footmark
of a certain type, `2` for the second, and so on. 

Once you've added this footnote marker, you'll need to also add the footnote itself. 
You do this with the `footnote` function. In this function, you can add a vector 
the same length as the number of footnotes of that type (alphabet, symbol, or number)
with the footnote text in order. 

For a simple example, the following code will add a single footnote for a single 
column header, using a symbol to denote the footnote:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, 
        col.names = c("State", 
                      paste0("Total Pertussis Cases", footnote_marker_symbol(1))),
        escape = FALSE) %>% 
  footnote(symbol = "Includes all cases for 1928--2011")
```

Here is an example of adding footnotes to two column names, using alphabetical symbols:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, 
        col.names = c(paste0("State", footnote_marker_alphabet(1)), 
                      paste0("Total Pertussis Cases", footnote_marker_alphabet(2))),
        escape = FALSE) %>% 
  footnote(alphabet = c("Top 10 states in terms of total case counts.",
                        "Includes all cases for 1928--2011."))
```
