## Change column names

### Basics of changing column names

By default, each column will have the same name as the column name in the data
that is input to `kable`. You can easily change those, though, with the 
`col.names` option. You just put in a character vector with as many values as you 
have columns, giving the names you would prefer:

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) 
```

### Changing formatting in column names

The `kableExtra` package includes a `row_spec` function. This will make changes to 
the formatting of a specific row in the table. 

You can use this for any row, and that includes the row with the column headers. 
The `kableExtra` conventions consider this as row 0.

For example, you can put the column headers in italics by setting `italic = TRUE`
in a `row_spec` call for row 0: 

```{r}
top_10_data %>% 
  kable(booktabs = TRUE, col.names = c("State", "Total Pertussis Cases")) %>% 
  row_spec(row = 0, italic = TRUE)
```

### Adding footnotes to column names
